fl0w - a development environment for the\\ KIPR Wallaby

### 2017-03-30 paper.tex
Write something about disc0very

\subsection{disc0very}
disc0very is the networked controller discovery protocol of fl0w\cite{fl0w:Philip Trauner}. It utilizes UDP broadcasts to find and advertise controllers.

>>>>

\subsection{disc0very}
disc0very is the controller discovery protocol of fl0w\cite{fl0w:Philip Trauner}. It utilizes UDP broadcasts to find and advertise controllers. It enables all fl0w\cite{fl0w:Philip Trauner} clients to connect together all the different Wallaby\cite{Wallaby Controller:KIPR} controllers and Sublime Text 3\cite{Sublime Text 3:Sublime HQ} clients automatically without any user interaction.\\

\subsubsection{discovery process}
When fl0w starts up, discovery will at first listen for a certain timeout period for other controllers on the broadcast. If it detects a already running fl0w\cite{fl0w:Philip Trauner} server in the local network, it will simply connect to that server and become a regular client. If not, the controller itself will become the server and advertise it on the broadcast.
